\documentclass[withhyper, two column]{altacv}

\usepackage{multicol}
\geometry{
    left=.8cm,
    right=.8cm,
    top=.8cm,
    bottom=.8cm,
    columnsep=0.6cm}
\setlength{\parindent}{0pt}

%-----------------------------------------
% HEADER
%-----------------------------------------
\name{M. Javad Beigrezaee}
\tagline{Mechanical Engineer — Process \& Industrial Design}
\personalinfo{
  \email{mjbeigrezaee@outlook.com}\\
  \phone{+45 50 38 80 09}\\
  \location{Horsens, Denmark}\\
  \linkedin{linkedin.com/in/mjbeigrezaee}
}

\begin{document}
\makecvheader

%-----------------------------------------
% LEFT COLUMN
%-----------------------------------------
\cvsection{Profile}
Mechanical engineer with expertise in industrial and mechanical design, CAD modeling, and structural analysis. Experienced in translating complex engineering concepts into **production-ready designs**, creating assemblies and detailed documentation for manufacturing and installation. Skilled in collaborating with multidisciplinary teams, suppliers, and project managers to ensure high-quality solutions in process-oriented environments.

%-----------------------------------------
\cvsection{Skills}

\cvsubsection{Mechanical \& Industrial Design}
\begin{itemize}
 \item Mechanical assemblies, cabinets, fixtures, and production equipment
 \item CAD: Autodesk Inventor, SolidWorks, AutoCAD; parametric modeling
 \item Design for manufacturability, assembly, and industrial standards
 \item Piping \& process layout understanding; familiar with P\&ID concepts
 \item Prototype building, testing, and troubleshooting
\end{itemize}

\cvsubsection{Engineering Analysis \& Simulation}
\begin{itemize}
 \item FEA: ABAQUS, ANSYS; linear/nonlinear, composite and metallic structures
 \item Structural integrity assessment and failure analysis
 \item CFD \& thermo-mechanical simulations for industrial components
\end{itemize}

\cvsubsection{Programming \& Automation}
\begin{itemize}
 \item Python, MATLAB, Julia, C++ for automation and simulation workflows
 \item HPC simulations, parametric optimization, and data processing
\end{itemize}

\cvsubsection{Other}
\begin{itemize}
 \item Technical reporting, BOM, assembly instructions, and documentation
 \item Collaboration with suppliers, project managers, and cross-disciplinary teams
 \item Installation support, commissioning, and validation
\end{itemize}

\divider
\divider
\divider

%-----------------------------------------
\cvsection{Education}

\cvevent
  {M.Sc., Applied Mechanics}
  {Iran University of Science and Technology}
  {2017--2019}{}
\divider

\cvevent
  {Ph.D., Solid Mechanics \& Structures}
  {University of Trento, Italy}
  {2021--2025}{}

%-----------------------------------------
% RIGHT COLUMN
%-----------------------------------------
\cvsection{Experience}

\cvevent
  {Doctoral Researcher}
  {University of Trento}
  {2021--2025}{Italy}
\begin{itemize}
 \item Designed mechanical assemblies and lattice/composite components suitable for testing and manufacturing.
 \item Built and validated prototypes, producing technical reports and detailed BOMs.
 \item Developed parametric workflows to optimize mechanical components and assemblies for performance and manufacturability.
 \item Collaborated with cross-functional teams to ensure integration of designs into larger systems.
\end{itemize}

\divider

\cvevent
  {Research Assistant}
  {Iran University of Science and Technology}
  {2017--2019}{Iran}
\begin{itemize}
 \item Analyzed and optimized structural components for industrial applications.
 \item Supported testing, assembly, and validation of mechanical systems.
 \item Prepared comprehensive technical documentation for project delivery and installation.
 \item Coordinated with team members to ensure design feasibility and manufacturability.
\end{itemize}

%-----------------------------------------
\cvsection{Selected Projects}

\cvevent
  {Industrial Mechanical Design \& Prototyping}
  {Python, SolidWorks, COMSOL, ABAQUS}
  {2021--2025}{}
\begin{itemize}
 \item Designed and optimized mechanical components for assemblies and prototypes in industrial environments.
 \item Automated workflows to speed up FEA, design iterations, and documentation.
 \item Validated designs through testing, ensuring robustness, manufacturability, and installation readiness.
\end{itemize}

\divider


\end{document}
