\documentclass[11pt,a4paper]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{etaremune}

\pagenumbering{gobble} 

\title{Publications — Mohammad Javad Beigrezaee}
\date{}
\author{}

\begin{document}
\maketitle

\section*{Under Review}
\begin{etaremune}
    \item \textbf{M.~J.~Beigrezaee}, S.~K.~Jalali, D.~Misseroni, N.~M.~Pugno, 
    ``A Refined Gibson--Ashby Model for Functionally Graded Honeycombs with Random Irregularities,'' 
    \emph{International Journal of Mechanical Sciences}, under review.
    
    \item \textbf{M.~J.~Beigrezaee}, M.~Heshmati, S.~K.~Jalali, N.~M.~Pugno, 
    ``Wave propagation in honeycombs with functionally graded wall thickness and random lattice irregularities,'' 
    \emph{International Journal of Mechanical Sciences}, under review.
\end{etaremune}

\section*{Journal Papers (ISI)}
\begin{etaremune}
    \item S.~K.~Jalali, \textbf{M.~J.~Beigrezaee}, N.~M.~Pugno, 
    ``Physically based machine learning for multi-objective optimal design of partially recycled materials,'' 
    \emph{Journal of Cleaner Production}, 2025, https://doi.org/10.1016/j.jclepro.2025.147081
    
    \item S.~K.~Jalali, \textbf{M.~J.~Beigrezaee}, D.~Misseroni, N.~M.~Pugno, 
    ``A modified Gibson--Ashby model for functionally graded lattice structures,'' 
    \emph{Mechanics of Materials}, 2024, \linebreak https://doi.org/10.1016/j.mechmat.2023.104822
    
    \item S. K. Jalali, \textbf{M.~J.~Beigrezaee}, and N. M. Pugno, “Reporting a misunderstanding in relating the Young’s modulus to functionally graded porosity,” Composite Structures, vol. 281, p. 115007, Feb. 2022, https://doi.org/10.1016/j.compstruct.2021.115007
    
    \item S. K. Jalali, \textbf{M.~J.~Beigrezaee}, and N. M. Pugno, “Is it always worthwhile to resolve the governing equations of plate theories for graded porosity along the thickness?,” Composite Structures, vol. 256, p. 112960, Jan. 2021, https://doi.org/10.1016/j.compstruct.2020.112960
    
    \item \textbf{M.~J.~Beigrezaee}, M. R. Ayatollahi, B. Bahrami, and L. F. M. da Silva, “A new geometry for improving the strength of single lap joints using adherend notching technique,” Journal of Adhesion, vol. 97, no. 11, pp. 1004–1023, 2021, https://doi.org/10.1080/00218464.2020.1724787
    
    \item B. Bahrami, M. R. Ayatollahi, \textbf{M.~J.~Beigrezaee}, and L. F. M. da Silva, “Strength improvement in single lap adhesive joints by notching the adherends,” International Journal of Adhesion and Adhesives, vol. 95, no. June, p. 102401, 2019, https://doi.org/10.1016/j.ijadhadh.2019.102401
    
    \item \textbf{M.~J.~Beigrezaee}, M. R. Ayatollahi, B. Bahrami, and L. F. M. da Silva, “Failure load analysis in single lap joints - effect of adherend notching,” Engineering Failure Analysis, vol. 104, no. May, pp. 75–83, 2019, https://doi.org/10.1016/j.engfailanal.2019.05.020
    
    \item S. K. Jalali, \textbf{M.~J.~Beigrezaee}, and S. Hayati, “How does porosity affect the free vibration of single-layered graphene sheets?,” Superlattices and Microstructures, vol. 128, no. November 2018, pp. 221–242, 2019, https://doi.org/10.1016/j.spmi.2019.01.023
    
    \item S. K. Jalali, \textbf{M.~J.~Beigrezaee}, and N. M. Pugno,
    “Atomistic evaluation of the stress concentration factor of graphene sheets having circular holes,”
    Physica E: Low-Dimensional Systems and Nanostructures,
    vol. 93, no. January, pp. 318–323, Sep. 2017, \linebreak https://doi.org/10.1016/j.physe.2017.06.031.






\end{etaremune}

\section*{Other Publications (non-ISI)}
\begin{etaremune}
    \item B.~Bahrami, M.~R.~Ayatollahi, \textbf{M.~J.~Beigrezaee}, 
    ``Strength improvement by adherend notching and tapering,'' 
    \emph{Journal of Science and Technology of Composites}, 2020.
    
    \item S.~K.~Jalali, \textbf{M.~J.~Beigrezaee}, 
    ``Stress concentration factor of graphene sheets with elliptical vacancies,'' 
    \emph{Journal of Solid Mechanics}, 2019.
\end{etaremune}

\section*{Conference Proceedings}
\begin{etaremune}
    \item S.~K.~Jalali, \textbf{M.~J.~Beigrezaee}, N. Pugno, " Machine Learning-Based Optimization of Recycled Resources Integration in Virgin Materials: A Focus on Automotive Applications", \emph{UK Association for Computational Mechanics} (UKACM 2025), London, United Kingdom, 23 – 25 April 2025.
    \item \textbf{M.~J.~Beigrezaee}, S.~K.~Jalali, D. Misseroni, N. Pugno, " Nonlinear Mechanical Simulation of Spider Silk Composites for Enhanced Energy Absorption", \emph{26th International Conference of the Theoretical and Applied Mechanics} (ICTAM 2024), Daegu, Korea, 25 – 30 August 2024.
    \item \textbf{M.~J.~Beigrezaee}, S.~K.~Jalali, D. Misseroni, N. Pugno, "A Gibson-Ashby Model for Graded 2D Cellular Solids", \emph{XVII international conference in computational plasticity, fundamentals, and applications} (COMPLAS 2023), Barcelona, Spain, 5 – 7 September 2023.
    \item S.~K.~Jalali, \textbf{M.~J.~Beigrezaee}, N. M. Pugno, “Vibrational Analysis of Defected Circular Single-layered Graphene and Silicene Sheets Under Pre-strains”, \emph{25th International Congress of Theoretical and Applied Mechanics} (ICTAM 2021), Milan, Italy, 22 – 27 August 2021
    \item S.~K.~Jalali and \textbf{M.~J.~Beigrezaee}, "Molecular Dynamic Based Free Vibrational Analysis of Circular Single Layered Graphene Sheets, " \emph{5th International Conference on Advances in Mechanical Engineering} (ICAME 2019), Istanbul, Turkey, 17 – 19 December 2019.
    \item M. R. Ayatollahi, B. Bahrami, \textbf{M.~J.~Beigrezaee}, "Finite element analysis of a geometrically improved single lap joint," \emph{2nd International Conference on Structural Integrity and Durability} (ICSID 2018), Dubrovnik, Croatia, 2 – 5 October 2018.
\end{etaremune}

\end{document}
